draft_group-6

### 2025-12-06 draft_group-6.Rmd
updated final draft

- Linear Discriminant Analysis (LDA) — A generative model that assumes equal covariance matrices for each class and normally distributed predictors. LDA often performs well in structured tabular data.

- Quadratic Discriminant Analysis (QDA) — Similar to LDA, but allows each class to have its own covariance matrix, giving the model more flexibility.
- K-Nearest Neighbors (KNN) — A nonparametric method that makes predictions by finding the k most similar clients. It captures nonlinear relationships but can be sensitive to scaling and high-dimensional data.

>>>>

- K-Nearest Neighbors (KNN) — A nonparametric method that makes predictions by finding the k most similar clients. It captures nonlinear relationships but can be sensitive to scaling and high-dimensional data.
